\newpage\thispagestyle{empty}
\begin{quote}\footnotesize
SPDX-License-Identifier: GPL-3.0-or-later OR GFDL-1.3-or-later OR CC-BY-SA-4.0

Copyright \copyright{} {\the\year} Yaii-Project Org. \\
The program used to generating Yaii Manual PDF files, is free software: you can redistribute it and/or modify it under the terms of the GNU General Public License as published by the Free Software Foundation, either version 3 of the License, or (at your option) any later version. \\
This program is distributed in the hope that it will be useful, but WITHOUT ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the GNU General Public License for more details. \\
You should have received a copy of the GNU General Public License along with this program. If not, see \url{https://www.gnu.org/licenses/}.

The document is the text and image content of Yaii Manual, you may have a PDF file or a paper copy of it. The document source file (.tex) is also a part of the program mentioned above.

Permission is granted to copy, distribute and/or modify this document
under the terms of the GNU Free Documentation License, Version 1.3
or any later version published by the Free Software Foundation;
with no Invariant Sections, no Front-Cover Texts, and no Back-Cover Texts.
A copy of the license is included in the section entitled ``\hyperref[label_fdl]{GNU
Free Documentation License}''.

Permission is granted to copy, distribute and/or modify this document
under the terms of the Creative Commons Attribution-ShareAlike 4.0 International. To view a copy of this license, visit \url{https://creativecommons.org/licenses/by-sa/4.0/}

Contributors: \\
NWater<\href{mailto:nwater23@outlook.com}{nwater23@outlook.com}>
\end{quote}

\endinput
